\propertitle

### 2019-07-22 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-22T13:06:53+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The question, then, is \emph{which features of the maximum-entropy
  frequency distribution are typical of the majority of plausible frequency
  distributions?} We can only answer for sure by using the full-fledged
probability calculus. A more complete study (in preparation) with the first
data set reveals that most of the plausible frequency distributions have
these important features in common with the maximum-entropy one:
\begin{itemize}
\item all activities $\yA/N \gtrsim 5\%$ have practically zero frequencies;
\item there are two regions of activity levels with high frequencies,
  roughly separated by a trough of lower frequencies. The frequencies of
  the region on the left ($\yA/N \lesssim 1.8\%$) are higher than those of
  the region on the right ($\yA/N \gtrsim 1.8\%$).
\end{itemize}
But there are also differences. For example, many plausible frequency
distributions have three or four modes instead of just two; and these modes
are higher than those of the maximum-entropy distribution.

@@

The second point is that our degrees of belief about the frequency
distribution for the full network depend not only on the measured data in
the sample, but also on our pre-data beliefs $\yI$ about the distribution.
Which assumptions lead to the maximum-entropy result? This distribution
appear when our initial belief about the possible frequency distributions
$\yF$ is quantified by an entropic prior
\citep{neumann2007,rodriguez1991,skilling1998,catichaetal2004,portamana2017}:
\begin{equation}
  \label{eq:entropic_prior}
  \pf(\yF \| \yI) \propto  \exp[-\yL\;\re(\yF;\yR)]
  \approx \binom{L}{L\yFF_{0}, \dotsc, L\yFF_{N}}\;
  \prod_{\yA}{\yRR_{\yA}}^{L\yFF_{\yA}}
\end{equation}
where $\re(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln(\yFF_{\yA}/\yRR_{\yA})$
is the relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is the
reference distribution, and $\yL$ a positive parameter. The approximate
equality (obtained through Stirling's approximation) shows that this prior
belief is proportional to the number of ways in which the distribution $\yF$
can be realized in $L$ time bins. The parameter $L$ roughly quantifies how
many time bins our data set must have to affect our initial belief.

@@

These results caution us against taking maximum-entropy solutions too
literally. The full probabilistic analysis allows us to see more clearly
the extent of our uncertainty and to make better-informed guesses.

\clearpage
\hrule
OLD TEXT
\hrule

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\iffalse
\begin{acknowledgements}
  PGLPM thanks Mari, Miri, \amp\ Emma for continuous encouragement and
  affection; Buster Keaton and Saitama for filling life with awe and
  inspiration; the developers and maintainers of \LaTeX, Emacs, AUC\TeX,
  Open Science Framework, Python, Inkscape, Sci-Hub for making a free and
  unfiltered scientific exchange possible.
%\rotatebox{15}{P}\rotatebox{5}{I}\rotatebox{-10}{P}\rotatebox{10}{\reflectbox{P}}\rotatebox{-5}{O}.
\sourceatright{\autanet}
\end{acknowledgements}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\clearpage
% %\renewcommand*{\appendixpagename}{Appendix}
% %\renewcommand*{\appendixname}{Appendix}
% %\appendixpage
% \appendix

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-22T13:24:52+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The question, then, is \emph{which features of the maximum-entropy
  frequency distribution are typical of the majority of plausible frequency
  distributions?} We can only answer for sure by using the full-fledged
probability calculus. A more complete study (in preparation) with the first
data set reveals that most of the plausible frequency distributions have
three important features in common with the maximum-entropy one:
\begin{itemize}
\item all activities $\yA/N \gtrsim 5\%$ have practically zero frequencies;
\item there are two regions of activity levels with high frequencies,
  roughly separated by a trough of lower frequencies.
\item The frequencies of the region on the left ($\yA/N \lesssim 1.8\%$)
  are higher than those of the region on the right ($\yA/N \gtrsim 1.8\%$).
\end{itemize}
But there are also differences. For example, many plausible frequency
distributions have three or four modes instead of just two; these modes are
higher than those of the maximum-entropy distribution; and the bump of high
frequencies on the right is slightly shifted towards lower activities than
the corresponding maximum in the maximum-entropy distribution.

@@

The second point is that our degrees of belief about the frequency
distribution for the full network depend not only on the measured data in
the sample, but also on our pre-data beliefs $\yI$ about the distribution.
Which assumptions lead to the maximum-entropy result? This distribution
appears when our initial belief about the possible frequency distributions
$\yF$ is quantified by an entropic prior
\citep{neumann2007,rodriguez1991,skilling1998,catichaetal2004,portamana2017}:
\begin{equation}
  \label{eq:entropic_prior}
  \pf(\yF \| \yI) \propto  \exp[-\yL\;\re(\yF;\yR)]
  \approx \binom{L}{L\yFF_{0}, \dotsc, L\yFF_{N}}\;
  \prod_{\yA}{\yRR_{\yA}}^{L\yFF_{\yA}}
\end{equation}
where $\re(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln(\yFF_{\yA}/\yRR_{\yA})$ is
the relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is the
reference distribution, and $\yL$ a positive parameter. The approximate
equality (obtained through Stirling's approximation), where the large
parentheses denote a multinomial coefficient, shows that this prior belief
is proportional to the number of ways in which the distribution $\yF$ can
be realized in $L$ time bins. The parameter $L$ roughly quantifies how many
time bins our data set must have to affect our initial belief. The
maximum-entropy approximation is valid when $L$ is large, but small
compared to the sharpness of the constraints on $\yF$; in our case this
means $\yL \approx 10$, give or take an order of magnitude.

We could obviously consider pre-data beliefs different
from~\eqref{eq:entropic_prior}, for example one quantified by a Dirichlet
distribution (which is equivalent to the above but with $\yF$ and $\yR$
switched), or a uniform distribution in $\yF$-space. Would these lead to
markedly different post-data beliefs? A full-fledged probabilistic analysis
shows that the three typical features listed above still appear with these
different initial beliefs. They are therefore robust.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{acknowledgements}
  This work is financially supported by the Kavli Foundation and the Centre
  of Excellence scheme of the  Research Council of Norway (Yasser Roudi group).\\
  PGLPM thanks Mari, Miri, \amp\ Emma for continuous encouragement and
  affection; Buster Keaton and Saitama for filling life with awe and
  inspiration; the developers and maintainers of \LaTeX, Emacs, AUC\TeX,
  Open Science Framework, Python, Inkscape, Sci-Hub for making a free and
  unfiltered scientific exchange possible.
%\rotatebox{15}{P}\rotatebox{5}{I}\rotatebox{-10}{P}\rotatebox{10}{\reflectbox{P}}\rotatebox{-5}{O}.
%\sourceatright{\autanet}
\end{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%\clearpage
% %\renewcommand*{\appendixpagename}{Appendix}
% %\renewcommand*{\appendixname}{Appendix}
% %\appendixpage
% \appendix

\hrule
OLD TEXT
\hrule

@@
